Comparison of Terrain Following and Cut Cell Grids using a Non-Hydrostatic Model

### 2015-10-20 src/tf-cutcell-comparison/fig-thermalAdvection.tex
split thermalAdvection plot into separate figure

\documentclass{article}
\usepackage{showframe}
\usepackage[paperwidth=6.2in,paperheight=2.3in,margin=0in]{geometry}
\usepackage{mathptmx}%{times}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[absolute,overlay]{textpos}
\usepackage{color}

\setlength{\parindent}{0pt}
\begin{document}
\centering
\includegraphics[width=6in]{../gravityWaves-btf-250m-300dz/18000/thetaDiffOverview.pdf}
\vspace*{0.1in}

\newpage
500m GW

\includegraphics[width=3in]{../gravityWaves-btf-250m-500dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-500dz/18000/thetaDiffMountain.pdf}

500m adv

\includegraphics[width=3in]{../thermalAdvection-btf-250m-500dz/18000/tracerDiffMountain.pdf}
\includegraphics[width=3in]{../thermalAdvection-cutCell-250m-500dz/18000/tracerDiffMountain.pdf}

\newpage
300m GW

\includegraphics[width=3in]{../gravityWaves-btf-250m-300dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-300dz/18000/thetaDiffMountain.pdf}

300m adv

\includegraphics[width=3in]{../thermalAdvection-btf-250m-300dz/18000/tracerDiffMountain.pdf}
\includegraphics[width=3in]{../thermalAdvection-cutCell-250m-300dz/18000/tracerDiffMountain.pdf}

\newpage
200m GW

\includegraphics[width=3in]{../gravityWaves-btf-250m-200dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-200dz/18000/thetaDiffMountain.pdf}

200m adv

\includegraphics[width=3in]{../thermalAdvection-btf-250m-200dz/18000/tracerDiffMountain.pdf}
\includegraphics[width=3in]{../thermalAdvection-cutCell-250m-200dz/18000/tracerDiffMountain.pdf}

\newpage
150m GW

\includegraphics[width=3in]{../gravityWaves-btf-250m-150dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-150dz/18000/thetaDiffMountain.pdf}

150m adv

\includegraphics[width=3in]{../thermalAdvection-btf-250m-150dz/18000/tracerDiffMountain.pdf}
\includegraphics[width=3in]{../thermalAdvection-cutCell-250m-150dz/18000/tracerDiffMountain.pdf}

\newpage

125m GW

\includegraphics[width=3in]{../gravityWaves-btf-250m-125dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-125dz/18000/thetaDiffMountain.pdf}

125m adv

\includegraphics[width=3in]{../thermalAdvection-btf-250m-125dz/18000/tracerDiffMountain.pdf}
\includegraphics[width=3in]{../thermalAdvection-cutCell-250m-125dz/18000/tracerDiffMountain.pdf}

\newpage

100m GW

\includegraphics[width=3in]{../gravityWaves-btf-250m-100dz/18000/thetaDiffMountain.pdf}
\includegraphics[width=3in]{../gravityWaves-cutCell-250m-100dz/18000/thetaDiffMountain.pdf}

100m adv

\includegraphics[width=3in]{../thermalAdvection-btf-250m-100dz/18000/tracerDiffMountain.pdf}
\includegraphics[width=3in]{../thermalAdvection-cutCell-250m-100dz/18000/tracerDiffMountain.pdf}

\newpage

50m adv

\includegraphics[width=3in]{../thermalAdvection-btf-250m-50dz/18000/tracerDiffMountain.pdf}
\includegraphics[width=3in]{../thermalAdvection-cutCell-250m-50dz/18000/tracerDiffMountain.pdf}

\end{document}

>>>>

\documentclass{article}
\usepackage{showframe}
\usepackage[paperwidth=3.1in,paperheight=3.2in,margin=0in]{geometry}
\usepackage{mathptmx}%{times}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage[absolute,overlay]{textpos}
\usepackage{color}

\setlength{\parindent}{0pt}
\begin{document}
\TPMargin{3pt}
\textblockcolour{white}
\begin{textblock}{0.75}(2.2,0.4)
\normalsize
\centering
(a)
\end{textblock}
\begin{textblock}{0.75}(2.2,8.4)
\normalsize
\centering
(b)
\end{textblock}
\centering
\includegraphics[width=3in]{../thermalAdvection-btf-250m-50dz/18000/tracerDiffMountain.pdf} \\
\vspace*{0.1in}
\includegraphics[width=3in]{../thermalAdvection-cutCell-250m-50dz/18000/tracerDiffMountain.pdf}
\end{document}
